A numerical study of fixation probabilities for strategies in the Iterated Prisoner's Dilemma

### 2017-04-10 tex/main.tex
Add section describing methodology.

% Packages
\usepackage[margin=1.5cm, includefoot, footskip=30pt]{geometry}
\usepackage{hyperref}

% Title
\title{A numerical study of fixation probabilities for strategies in the
Iterated Prisoner's Dilemma}
\author{Marc Harper and Vincent Knight}
\date{}

@@

I think we'd want to include a few of the heatmaps in the final section of the notebook for some interesting cases, like FoolMeOnce, EvolvedLookerUp, etc. Pushing N higher will make all the plots more interesting. How high we can get N? I'd really like to get it to N >= 12.

@@

@@

\bibliographystyle{plain}
\bibliography{./bibliography.bib}
\end{document}

>>>>

% Packages
\usepackage[margin=1.5cm, includefoot, footskip=30pt]{geometry}
\usepackage{hyperref}
\usepackage{multicol}
\usepackage{booktabs}
\usepackage{xstring}
\usepackage{subcaption}
\usepackage{graphicx}

% Title
\title{A numerical study of fixation probabilities for strategies in the
Iterated Prisoner's Dilemma}
\author{Marc Harper \and Vincent Knight}
\date{}

@@

Ip think we'd want to include a few of the heatmaps in the final section of the
notebook for some interesting cases, like FoolMeOnce, EvolvedLookerUp, etc.
Pushing N higher will make all the plots more interesting. How high we can get
N? I'd really like to get it to N >= 11.

@@

\section{Methodology}\label{sec:methodology}

To carry out this large numerical experiment 172 strategies are used from
\cite{axelrodproject}. These include 169 default strategies in the library at
the time (excluding strategies classified as having a long run time) as well as
the following 3 finite state machine strategies:

% TODO Include details about the 3 extra FSM strategies.

Appendix~\ref{app:list_of_players} shows all the players in question. More
information about each player can be obtained in the documentation for
\cite{axelrodproject}. The memory depth of the used strategies is shown in
Table~\ref{tbl:memory_depth_count}.

\begin{table}[!hbtp]
    \centering
        \begin{subfigure}[t]{\textwidth}
            \centering
                \input{../tbl/memory_depth_count.tex}
                \caption{Memory depth}
                \label{tbl:memory_depth_count}
        \end{subfigure}
        \vspace{.5cm}

        \begin{subfigure}[t]{\textwidth}
            \centering
                \input{../tbl/stochastic_count.tex}
                \caption{Stochastic versus deterministic}
                \label{tbl:stochastic_count}
        \end{subfigure}
        \caption{Summary of properties of used strategies}
\end{table}

All strategies are paired and these pairs are used in 1000 repetitions of a
Moran process assuming a starting population of \((N/2, N/2)\). This is repeated
for even \(N\) between 2 and 14. The fixation probability is then estimated for
each value of \(N\).

Note that due to the high computational cost of these experiments, for any given
interaction between two players within the Moran process the outcome is sampled
from a pre computed cache of 10000 match outcomes. This is carried out using the
approximate Moran process implemented in \cite{axelrodproject}.

As an example, Figure~\ref{fig:players_with_most_scores} shows the scores
between two players that over the 10000 outcomes gives 6817 different scores.

\begin{figure}[!htbp]
    \centering
    \includegraphics[width=.4\textwidth]{../img/players_with_most_scores.pdf}
    \caption{All possible scores for the pair of strategies that have the most
    different number of match outcomes}
    \label{fig:players_with_most_scores}
\end{figure}

@@

\bibliographystyle{plain}
\bibliography{./bibliography.bib}

\appendix

\section{List of players}\label{app:list_of_players}

\begin{multicols}{3}
	\begin{enumerate}
		\input{../tbl/list_of_players.tex}
	\end{enumerate}
\end{multicols}

\end{document}
